---
title: "Analysis Linear Models"
output:
  html_document:
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
params:
  d_to_model: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading, setting up

```{r, load-packages, message = FALSE}
library(tidyverse)
library(lme4)

d_to_model <- params$d_to_model
```

# State-level descriptives

```{r}
distinct_states <- d_to_model %>% 
  distinct(state, .keep_all = TRUE) %>% 
  select(-user_id, -screen_name, -created_at)
```

## Descriptives

```{r}
distinct_states %>% 
  select(n_tweets_at_state_level,
         voices, 
         national_school_lunch_program_fy_2016_fns_usda_gov,
         pct_students_frpl, 
         state_spending_on_public_elementary_secondary_spending_fy_2016_census_in_thousands,
         state_spending_per_child,
         urban_percentage_of_state_population_in_2015,
         three_year_average_of_state_poverty_rates_2015_2017,
         teacher_salaries_nea_2016,
         c_ideology,
         g_ideology,
         region_by_census,
         enrollment_in_public_ele_sec_education_digest_of_ed_stats_fall_2015_projected,
         full_time_equivalent_fte_teachers_state_2015_16,
         full_time_equivalent_fte_staff_state_2015_16,
         pct_students_frpl,
         total_students_state_2015_16,
         staff_teachers,
         coordinators_teachers
  ) %>% 
  skimr::skim()
```

## Correlations

```{r}
distinct_states %>% 
  select(n_tweets_at_state_level,
         voices, 
         national_school_lunch_program_fy_2016_fns_usda_gov,
         pct_students_frpl, 
         state_spending_on_public_elementary_secondary_spending_fy_2016_census_in_thousands,
         state_spending_per_child,
         urban_percentage_of_state_population_in_2015,
         three_year_average_of_state_poverty_rates_2015_2017,
         teacher_salaries_nea_2016,
         c_ideology,
         g_ideology,
         region_by_census,
         enrollment_in_public_ele_sec_education_digest_of_ed_stats_fall_2015_projected,
         full_time_equivalent_fte_teachers_state_2015_16,
         full_time_equivalent_fte_staff_state_2015_16,
         pct_students_frpl,
         total_students_state_2015_16,
         staff_teachers,
         coordinators_teachers
  ) %>% 
  corrr::correlate() %>% 
  corrr::shave() %>% 
  corrr::fashion() 
```

## Analysis

What stands out here for relating to `mean_n_tweets_by_user_in_state`?

- Voices (unique users) matters a great deal
- both ideology measures (congress and governor) seem to matter, but are highly correlated (r = .79)
- free and reduced price lunch percentage seems important
- teacher salaries

## Some linear models

```{r, state-level-models}
m_state_level <- glm(n_tweets_at_state_level ~ 1 + 
                       
                       scale(voices) + 
                       
                       scale(c_ideology) + 
                       scale(g_ideology) + 
                       
                       three_year_average_of_state_poverty_rates_2015_2017 +
                       pct_students_frpl +
                       
                       state_spending_per_child +
                       total_students_state_2015_16 +
                       
                       full_time_equivalent_fte_teachers_state_2015_16 +
                       
                       scale(urban_percentage_of_state_population_in_2015), 
                     data = distinct_states, 
                     family = "poisson")

sjPlot::tab_model(m_state_level, show.std = "std2")
performance::check_model(m_state_level)
```

What can we take away from these?

**key takeaways predicting the number of tweets at the state level**
- more voices mean more tweets
- ideology matters a lot, with right leaning seeing greater activity

**key takeaways from below**
- ideology, poverty matter, with poorer, more right-leaning states seeing more activity
- those who have been on Twitter longer are more active
- states with higher unemployment see more activity
