---
title: "Analysis Multi-Level Models"
output:
  html_document:
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

## Loading, setting up

```{r, load-packages, message = FALSE}
d_to_model <- read_csv("data/d-to-model.csv")
```

## Descriptives

```{r}
d_to_model %>% 
  select(n_tweets_at_state_level,
         voices, 
         national_school_lunch_program_fy_2016_fns_usda_gov,
         pct_students_frpl, 
         state_spending_on_public_elementary_secondary_spending_fy_2016_census_in_thousands,
         state_spending_per_child,
         urban_percentage_of_state_population_in_2015,
         three_year_average_of_state_poverty_rates_2015_2017,
         teacher_salaries_nea_2016,
         c_ideology,
         g_ideology,
         region_by_census,
         enrollment_in_public_ele_sec_education_digest_of_ed_stats_fall_2015_projected,
         staff_teachers,
         coordinators_teachers
  ) %>% 
  skimr::skim()
```

## Correlations

```{r}
d_to_model %>% 
  select(n_tweets_at_state_level,
         voices, 
         national_school_lunch_program_fy_2016_fns_usda_gov,
         pct_students_frpl, 
         state_spending_on_public_elementary_secondary_spending_fy_2016_census_in_thousands,
         state_spending_per_child,
         urban_percentage_of_state_population_in_2015,
         three_year_average_of_state_poverty_rates_2015_2017,
         teacher_salaries_nea_2016,
         c_ideology,
         g_ideology,
         region_by_census,
         enrollment_in_public_ele_sec_education_digest_of_ed_stats_fall_2015_projected,
         staff_teachers,
         coordinators_teachers
  ) %>% 
  corrr::correlate() %>% 
  corrr::shave() %>% 
  corrr::fashion() 
```

# Analysis - at the individual level 

```{r, model-4, eval = TRUE}
m4 <- glmer(n_tweets ~ 1 + 
              
              # individual
              #scale(favorite_count) +
              scale(time_of_account) + 
              
              # state-level
              scale(c_ideology) + 
              scale(three_year_poverty_rates) + 
              scale(pct_urban_in_state) +
              
              scale(voices) + scale(unemployment) + 
              
              scale(state_spending) + 
              
              
              (1|hashtag), 
            data = d_to_model,
            family = "poisson")

performance::icc(m4)
sjPlot::tab_model(m4, show.std = TRUE)
```

- ideology, poverty matter, with poorer, more right-leaning states seeing more activity
- those who have been on Twitter longer are more active
- states with higher unemployment see more activity

# Takeaways

**For predicting more users at the state level**:
- Voices matter a great deal positively
- Less urban, more right-leaning states with more users

**For predicting how active users are**
- How long someone has been on Twitter and how many Tweets they've posted seems to be associated with greater activity, though I think we need to talk and think through the logic of these
- Poorer, more right-leaning states are associated with more activity
